\Large \bf \projtitle

### 2015-05-08 doc/paper/paper.tex
Fix

\zbf is an open-sourced system that will allow developers to easily utilize
a peer-to-peer CDN to increase the content delivery bandwidth of their sites,
even when operating under heavy request loads. Preliminary data shows that
the system performs well under medium and high workloads, and when the
seeder-to-leecher ratio is high. Future work could refine the system
such that it works well in a wide variety of scenarios. Our results show that peer-to-peer
CDNs are a promising low-cost alternative to CDNs that require on an extensive
network of server and server infrastructure.

>>>>

\zbf is an open-sourced system that will allow developers to easily utilize a
peer-to-peer CDN to increase the content delivery bandwidth of their sites,
even when operating under heavy request loads. Preliminary data shows that the
system performs well under medium and high workloads, and when the
seeder-to-leecher ratio is high. Future work could refine the system such that
it works well in a wide variety of scenarios. Our results show that
peer-to-peer CDNs are a promising low-cost alternative to CDNs that require an
extensive network of server and server infrastructure.
